(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-26 ms.tex
SDSS background object text, TRES skeleton

\newcommand{\todo}[3]{{\color{#2} \emph{#1} TO DO: #3}}
\newcommand{\btmtodo}[1]{\todo{BEN}{red}{#1}}

@@

In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness...

@@

@@

Something about Multis and TTVs.

>>>>

\newcommand{\todo}[3]{{\color{#2} \emph{#1} TO DO: #3}}
\newcommand{\btmtodo}[1]{\todo{BEN}{red}{#1}}
\newcommand{\anytodo}[1]{\todo{ANYONE}{NavyBlue}{#1}}

@@

In Table \ref{Table:BGstars}, the ``maximum depth'' column represents
the maximum observed ``transit'' depth if the transit were actually caused
by a total eclipse of the hypothetical background binary system, inducing
a 50\% flux decrement in the background star's apparent brightness.

For EPIC 201465501 and 201779067, the observed transit depth is 
larger than each of these values, so we reject the possibility that
these events could be the eclipses of the background binaries detected
here.

For EPIC 201546283, the observed transit depth is nearly identical to 
the maximum false positive depth. 
The photometry for this potential contaminant is consistent with that
of an M3V star; for this object to cause the observed eclipse it must
be a total eclipse of two M3V stars. 
However, in that case, the observed event would be exactly V-shaped,
with second and third contact occurring simultaneously. 
Since the transit is not V-shaped, it must be the result of
a relatively small body passing in front of a relatively large body. 
Therefore, it cannot be caused by this observed background dwarf star.

For EPIC 201295312, the transit depth is significantly shallower than
the maximum false positive depth, so we cannot immediately
reject the hypothesis that the transit is actually a false positive 
induced by a background eclipsing binary. \anytodo{Can we place limits
on this possibility from the lack of a centroid shift?}

SDSS is 95\% complete at $r=22.2$ and the telescope has a point
spread function of $1\farcs4$. In all cases except the four above, we 
treat the SDSS data as providing a contrast curve at wide separations
down to a limiting magnitude of $r=22.2$.

@@

We observed EPIC 201912552 on (all UT) February 04 2015, February 24 2015,
and February \btmtodo{XX} 2015 with the Tillinghast Reflector Echelle
Spectrograph (TRES) on the 1.5 m Tillinghast Reflector at the Fred L.
Whipple Observatory. 
The spectra were taken with a resolving power of $R=44,000$ and 
integration times ranging from 2800 to 3600 seconds, resulting in 
signal-to-noise ratios between 17 and 29 per resolution element.

\anytodo{This will be text from DaveL and/or Allyson Bieryla.}

The observed radial velocities are included in Table \ref{Tab:RVs}.

\btmtodo{RVs table}

%57057.83314
%57077.75616

@@

Something about Multis and TTVs will go in here.

\anytodo{We should have a figure of many subplots, of phase-folded
transits for all the confirmed planets. 
To ease Dan's mind, we will say that they are the product of 
some fidicual transit model and are only presented here for illustrative
purposes.}
